INGRID: Creating Languages in MPS from ANTLR Grammars

### 2017-06-07 paper.tex
new format

\documentclass[preprint,10pt,numbers]{sigplanconf}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{url}
\usepackage{xspace}
\usepackage{listings}
\usepackage[noline]{algorithm2e}
\usepackage{comment}
\usepackage{color}
\usepackage{times}
\usepackage{multirow}
\usepackage{balance}
\usepackage{framed}
\usepackage{alltt}
\usepackage{textcomp}
\usepackage[dvipsnames]{xcolor}

@@

@@

% coloring and font style commands
  % ANTLR
\newcommand{\antlrap}{\textquotesingle}
\newcommand{\antlrparserrule}[1]{\textcolor{Blue}{#1}}
\newcommand{\antlrlexerrule}[1]{\textcolor{BrickRed}{#1}}
\newcommand{\antlrliteralnoap}[1]{\textcolor{Maroon}{#1}}
\newcommand{\antlrliteral}[1]{\antlrap\antlrliteralnoap{#1}\antlrap}
\newcommand{\antlrregex}[1]{\textcolor{OliveGreen}{#1}}
  % MPS in general
\newcommand{\mpsconcept}[1]{\textcolor{OliveGreen}{#1}}
\newcommand{\mpsinterface}[1]{\textcolor{Plum}{#1}}
  % MPS structure
\newcommand{\mpsstkeyword}[1]{\textcolor{Blue}{\textbf{#1}}}
\newcommand{\mpsstalias}[1]{\textcolor{Green}{\textbf{#1}}}
\newcommand{\mpsstproperty}[1]{\textcolor{Fuchsia}{\textbf{#1}}}
\newcommand{\mpsstplaceholder}[1]{\textcolor{Gray}{\textbf{#1}}}
\newcommand{\mpsstcardinality}[1]{\textcolor{RoyalBlue}{\textbf{#1}}}
  % MPS editor
\newcommand{\mpsedkeyword}[1]{\textcolor{Black}{\textbf{#1}}}
\newcommand{\mpsedtarget}[1]{\textcolor{RubineRed}{\textbf{#1}}}
\newcommand{\mpsedannotation}[1]{\textcolor{Gray}{\textbf{#1}}}
  % MPS textgen
\newcommand{\mpstgkeyword}[1]{\textcolor{Blue}{\textbf{#1}}}
\newcommand{\mpstgtarget}[1]{\textcolor{RubineRed}{\textbf{#1}}}
\newcommand{\mpstgparam}[1]{\textcolor{RoyalPurple}{\textbf{#1}}}
\newcommand{\mpstgaction}[1]{\textcolor{Fuchsia}{\textbf{#1}}}
\newcommand{\mpstgliteral}[1]{\textcolor{Green}{\textbf{#1}}}
\newcommand{\mpstgnodeprop}[1]{\textcolor{darkgray}{\textbf{#1}}}

@@

% TODO
%\conferenceinfo{PLDI '17}{June 19--26, 2017, Barcelona, Spain}
%\copyrightyear{20yy}
%\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
%\copyrightdoi{nnnnnnn.nnnnnnn}

% TODO
%\publicationrights{licensed}

@@

\authorinfo{P\v{r}emysl Vysok\'y \and Pavel Par\'izek}
	{Charles University, Faculty of Mathematics and Physics, Prague, Czech Republic}
	{premek.vysoky@gmail.com, parizek@d3s.mff.cuni.cz}

\authorinfo{V\'aclav Pech}
	{JetBrains}
	{vaclav@jetbrains.com}

@@

\category{D.3.2}{Language Classifications}{Extensible languages}
\category{D.3.4}{Processors}{Parsing}
\category{D.3.4}{Processors}{Code generation}
\category{D.2.3}{Coding Tools and Techniques}{Program editors}

\terms
Languages

\keywords
language workbench, projectional editor, grammar, domain-specific language, ANTLR, JetBrains MPS

@@

\acks
% TODO mozna pridat jeste nejaky dalsi grant (az clanek nekam vezmou)
This work was partially supported by JetBrains.

>>>>

\documentclass[sigplan,10pt,preprint]{acmart}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{url}
\usepackage{xspace}
\usepackage{listings}
\usepackage[noline]{algorithm2e}
\usepackage{comment}
\usepackage{color}
\usepackage{multirow}
\usepackage{balance}
\usepackage{framed}
\usepackage{alltt}
\usepackage{xcolor}

@@

\settopmatter{printfolios=true}

@@

% coloring and font style commands
  % ANTLR
\newcommand{\antlrap}{\textquotesingle}
\newcommand{\antlrparserrule}[1]{\textcolor{blue}{#1}}
\newcommand{\antlrlexerrule}[1]{\textcolor{red}{#1}}
\newcommand{\antlrliteralnoap}[1]{\textcolor{orange}{#1}}
\newcommand{\antlrliteral}[1]{\antlrap\antlrliteralnoap{#1}\antlrap}
\newcommand{\antlrregex}[1]{\textcolor{olive}{#1}}
  % MPS in general
\newcommand{\mpsconcept}[1]{\textcolor{olive}{#1}}
\newcommand{\mpsinterface}[1]{\textcolor{violet}{#1}}
  % MPS structure
\newcommand{\mpsstkeyword}[1]{\textcolor{blue}{\textbf{#1}}}
\newcommand{\mpsstalias}[1]{\textcolor{olive}{\textbf{#1}}}
\newcommand{\mpsstproperty}[1]{\textcolor{violet}{\textbf{#1}}}
\newcommand{\mpsstplaceholder}[1]{\textcolor{gray}{\textbf{#1}}}
\newcommand{\mpsstcardinality}[1]{\textcolor{cyan}{\textbf{#1}}}
  % MPS editor
\newcommand{\mpsedkeyword}[1]{\textcolor{black}{\textbf{#1}}}
\newcommand{\mpsedtarget}[1]{\textcolor{magenta}{\textbf{#1}}}
\newcommand{\mpsedannotation}[1]{\textcolor{gray}{\textbf{#1}}}
  % MPS textgen
\newcommand{\mpstgkeyword}[1]{\textcolor{blue}{\textbf{#1}}}
\newcommand{\mpstgtarget}[1]{\textcolor{magenta}{\textbf{#1}}}
\newcommand{\mpstgparam}[1]{\textcolor{violet}{\textbf{#1}}}
\newcommand{\mpstgaction}[1]{\textcolor{violet}{\textbf{#1}}}
\newcommand{\mpstgliteral}[1]{\textcolor{olive}{\textbf{#1}}}
\newcommand{\mpstgnodeprop}[1]{\textcolor{darkgray}{\textbf{#1}}}

% TODO
%\acmConference[PL'17]{ACM SIGPLAN Conference on Programming Languages}{January 01--03, 2017}{New York, NY, USA}
%\acmYear{2017}
%\acmISBN{978-x-xxxx-xxxx-x/YY/MM}
%\acmDOI{10.1145/nnnnnnn.nnnnnnn}

% TODO
%\setcopyright{acmlicensed}

@@

@@

\author{P\v{r}emysl Vysok\'y}
\affiliation{
  \institution{Charles University, Faculty of Mathematics and Physics}
  \city{Prague}
  \country{Czech Republic}
}
\email{premek.vysoky@gmail.com}

\author{Pavel Par\'izek}
\affiliation{
  \institution{Charles University, Faculty of Mathematics and Physics}
  \city{Prague}
  \country{Czech Republic}
}
\email{parizek@d3s.mff.cuni.cz}

\author{V\'aclav Pech}
\affiliation{
  \institution{JetBrains}
}
\email{vaclav@jetbrains.com}

@@

 \begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008.10011009.10011019</concept_id>
<concept_desc>Software and its engineering~Extensible languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011041.10011047</concept_id>
<concept_desc>Software and its engineering~Source code generation</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011066.10011069</concept_id>
<concept_desc>Software and its engineering~Integrated and visual development environments</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011041.10011688</concept_id>
<concept_desc>Software and its engineering~Parsers</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Extensible languages}
\ccsdesc[500]{Software and its engineering~Source code generation}
\ccsdesc[500]{Software and its engineering~Integrated and visual development environments}
\ccsdesc[300]{Software and its engineering~Parsers}

\keywords{language workbench, projectional editor, grammar, domain-specific language, ANTLR, JetBrains MPS}

@@

\begin{acks}
% TODO mozna pridat jeste nejaky dalsi grant (az clanek nekam vezmou)
This work was partially supported by JetBrains.
\end{acks}
